Northern Pikeminnow Abundance in Deadwater Slough, Salmon River, Idaho, and Potential Impacts to Local Chinook Salmon Populations

### 2022-04-04 analysis/paper/paper.Rmd
draft edits complete

juv_cons_p = impact_df %>%
  select(season,
         perc_diet,
         p_chnk,
         N = juv_N,
         Lci = juv_Lci,
         Uci = juv_Uci) %>%
  group_by(perc_diet,
           p_chnk) %>%
  summarise(across(c("N", "Lci", "Uci"),sum),
            .groups = "drop") %>%
  mutate(Stage = "Juveniles") %>%
  mutate(p_chnk = p_chnk * 100) %>%
  rename(perc_chnk = p_chnk) %>%
  ggplot(aes(x = perc_diet,
             y = N,
             group = as.factor(perc_chnk),
             color = as.factor(perc_chnk))) +
  geom_point(size = 2) +
  geom_line(size = 1.1) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  scale_color_manual(name = "Percent Chinook", 
                     values=c("lightsteelblue","steelblue3","navyblue")) +
  theme(axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.text.x = element_text(size = 11,
                                    color = "black"),
        strip.text.y = element_text(size = 11,
                                    color = "black"),
        legend.position = c(.19, .89),
        legend.background = element_blank(),
        legend.key.size = unit(.56, "cm"),
        legend.box = 'horizontal') +
  labs(y = "Estimated Juvenile Chinook Consumed", 
       x = "Percent Fish in Pikeminnow Diet")

>>>>

juv_cons_p = impact_df %>%
  select(season,
         perc_diet,
         p_chnk,
         N = juv_N,
         Lci = juv_Lci,
         Uci = juv_Uci) %>%
  group_by(perc_diet,
           p_chnk) %>%
  summarise(across(c("N", "Lci", "Uci"),sum),
            .groups = "drop") %>%
  mutate(Stage = "Juveniles") %>%
  mutate(p_chnk = p_chnk * 100) %>%
  rename(perc_chnk = p_chnk) %>%
  ggplot(aes(x = perc_diet,
             y = N / 1000,
             group = as.factor(perc_chnk),
             color = as.factor(perc_chnk))) +
  geom_point(size = 2) +
  geom_line(size = 1.1) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  scale_color_manual(name = "Percent Chinook", 
                     values=c("lightsteelblue","steelblue3","navyblue")) +
  theme(axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.text.x = element_text(size = 11,
                                    color = "black"),
        strip.text.y = element_text(size = 11,
                                    color = "black"),
        legend.position = c(.19, .89),
        legend.background = element_blank(),
        legend.key.size = unit(.56, "cm"),
        legend.box = 'horizontal') +
  labs(y = "Juvenile Chinook Consumed (x 1,000)", 
       x = "Percent Fish in Pikeminnow Diet")
